Detecting AI-Generated Images using ResNet

### 2022-12-13 paper/paper.tex
Update paper

\begin{document}
\maketitle
\begin{abstract}
  Abstract goes here.
\end{abstract}

@@

\subsubsection{Indoor Scene Recognition Dataset}

@@

\subsubsection{Weather Image Recognition Dataset}

@@

\subsubsection{Comic Books Images Dataset}

@@

\subsubsection{Image Variation Generation}

@@

@@

The main task of this project is classification. Over the years, researchers tend to make deeper neural networks(adding more layers) to solve such complex tasks and to also improve the classification accuracy. But, it has been seen that as we go adding on more layers to the neural network, it becomes difficult to train them and the accuracy starts saturating and then degrades also. Therefore, we decided to use ResNet, which overcomes the above issue, to do the classification.

@@

\textbf{Stable Diffusion model}

Weather Image Recognition Dataset: real-world weather pictures with their generated pictures.

Comic Books Images Dataset: comic book images with their generated pictures.

\textbf{Dalle2 model}

Weather Image Recognition Dataset: real-world weather pictures with their generated pictures.

>>>>

\begin{document}
\maketitle
\begin{abstract}
  Recent advances in diffusion models have set an impressive milestone in image-to-image generation tasks. Trending works such as DALL-E2 and Stable Diffusion have attracted great interest in academia and industry. However, there are lack of evaluation about the images generated by these methods. In this paper, we generate synthetic images with the "Stable Diffusion" image diffusion generation model. The mixed dataset is mixed with the synthetic images and the original images and used as training data and test data in machine learning applications to investigate the capabilities of the Stable Diffusion model. Analyses show that the model training with ResNet could distinguish between the synthetic images and the original images with very high accuracy.
\end{abstract}

@@

\subsubsection{Indoor Scene Recognition Dataset}
\label{sec:indoor_dataset}

@@

\subsubsection{Weather Image Recognition Dataset}
\label{sec:weather_dataset}

@@

\subsubsection{Comic Books Images Dataset}
\label{sec:comic_dataset}

@@

\subsubsection{Image Variation Generation}
\label{sec:datasets_image_variation_generation}

@@

By running CLIP-image-encoder-guided Stable Diffusion mentioned in Section \ref{sec:datasets_image_variation_generation} on our raw datasets, we built our main dataset from the indoor dataset in Section \ref{sec:indoor_dataset} which contains 15,621 real-world in-door photos and combined with another 15,621 generated images that are similar to the real-world photos. Aside from the main dataset, we also built two smaller datasets from the weather dataset in \ref{sec:weather_dataset} and the comic book dataset in \ref{sec:comic_dataset} for testing the model's generalization on other genres of photos. For each image in this dataset, we applied center-cropping and resizing postprocessing to make sure they are consistent in image size, being 256x256.

@@

The main task of this project is classification. Over the years, researchers tend to make deeper neural networks(adding more layers) to solve such complex tasks and to also improve the classification accuracy. But, it has been seen that as we go adding on more layers to the neural network, it becomes difficult to train them and the accuracy starts saturating and then degrades also. Therefore, we decided to use \textbf{ResNet}, which overcomes the above issue, to do the classification.

@@

\textbf{Stable Diffusion model:} In order to test the generalization ability of our Resnet34 model and to verify it really learns the features of Stable Diffusion generation, not any specific features of Indoor pictures, we use the same method to generate the following dataset which has different pictures contents than Indoor Scene Recognition Dataset:

(1) Weather Image Recognition Dataset: real-world weather pictures with generated pictures.

(2) Comic Books Images Dataset: comic book images with generated pictures.

\textbf{Dalle2 model: } Besides, we want to test whether the model can distinguish AI pictures generated by other methods. Thus, we choose the same Weather Image Recognition Dataset but generate AI picutres using Dalle2 model to test the performance.
